Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-02 introduction.tex
Add discussion feedbacks

With the newly developed techniques, we revisit the classical verification of quantum computation problems from both a philosophical and a practical point of view.
We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment.
Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of delegation for quantum sampling problems.
 %Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model,
However, it is far from clear whether the subtle difference between $\BQP$ and its sampling version could lead to
technical barrier in the context of CVQC, or
 %what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear.
whether one can develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.

@@

% \Ethan{Below is my attempt to talk about it in my SoP}

% It was proven that BQP=BQIP\hannote{who  when and cite}. That is, if a quantum computer can efficiently solve a given decision problem, then it can also efficiently convince a classical machine of its solution. I'm generalizing this to arbitrary efficient quantum computations. The proof for decision problems involves the classical verifier reducing the problem to a local Hamiltonian instance; the quantum prover would then commit its certificate and act as the verifier’s trusted measurement device as put forth in ``Classical Verification of Quantum Computations" by Mahadev. It isn't as trivial as it may seem. Repeating the scheme for each qubit loses the information carried by entanglements and throws off the joint distribution between qubits. Simply measuring the entire output register instead is difficult to analyze. For decision problems, it’s not hard to argue that a malicious prover cannot do better than sending identical copies of some pure state unentangled with each other. That same reasoning doesn't apply here a priori. I've been trying to get a grasp on the particular structure of the local Hamiltonian reduction in order to better analyze it.

% \Ethan{Below is my attempt to talk about it in my research proposal}

% We are interested in delegating quantum computations from a classical client to an untrusted quantum server. Under this setting, the client would send the server a quantum circuit and an initial state. Then, through interaction with the honest server, the client obtains a measurement result as if he measured the true output of the circuit. If the server attempts to deceive the client, the client should reject it. The case where the circuit encodes a decision problem has been well-studied, and we're now trying to generalize those results to circuits with possibly many bits of output.

% If the circuit encodes a decision problem, then by considering adiabatic quantum computation, there exists a reduction to local Hamiltonian. Local Hamiltonian is QMA-complete, so there's a certificate for every yes-instance, and no valid certificates for any no-instances. An introduction can be found in Kitaev, Shen, and Vyalyi's "Classical and Quantum Computation". Furthermore, Biamonte and Love's "Realizable Hamiltonians for Universal Adiabatic Quantum Computers" states that these local Hamiltonians have very simple forms, which in turn implies that in order to check such certificates one only requires abilities to receive qubits and perform X/Z measurements. Based on this observation, Mahadev constructed a protocol in "Classical Verification of Quantum Computations" which, under the LWE assumption (a widely believed conjecture in quantum cryptography), allows the prover to commit qubits and act as the verfier's trusted X/Z measurement device. This solves the delegation of decision problem from a fully classical client to a quantum server.

% To generalize delegation of quantum computations to allow long output, simply repeating the known protocol for every output qubit doesn't work. The joint probability distribution between qubits would be incorrect due to entanglements. In fact, generally the output qubits encode sampling problems rather than decision problems. Furthermore, for decision problems one can argue that the prover's optimal strategy is to send identical copies of a certificate, so Chernoff bound can be applied, but said argument doesn't generalize to sampling problems either. To overcome these challenges, we start by modifying the local Hamiltonian construction so it is compatible with long output. We then analyze our protocol's soundness more carefully, before using Mahadev's result as a black box to solve the long output case too for fully classical clients.

% A possible application for our long output protocol is to make the computation not only verifiable, but also private in the sense of homomorphic encryptions. That is, the input is encrypted before being sent to the server. The server computes on the encrypted input, obtaining an encrypted output. The client then receives and decrypts the output. Here we can combine results from Mahadev's "Classical Homomorphic Encryption for Quantum Circuits" with our long output scheme. The client can simply send the homomorphic evaluation circuit to the server with the encrypted input.

>>>>

With the newly developed techniques, we revisit the classical verification of quantum computation problems from both a philosophical and a practical point of view.
We first observe that the \emph{sampling} version of $\BQP$ (e.g., the class $\SampBQP$ formulated by Aaronson~\cite{aaronson_2013}) might be a more appropriate notion to serve the purpose of the original problem.
Philosophically, the outcomes of quantum mechanical experiments are usually samples or statistical information, which is well demonstrated in the famous double-slit experiment.
Moreover, a lot of quantum algorithms from Shor's~\cite{Shor} and Grover's~\cite{Grover} algorithms to some recent developments in machine learning and optimization (e.g.~\cite{brando_et_al:LIPIcs:2019:10603, AGGW17,pmlr-v97-li19b}) contain a significant quantum sampling component.
The fact that almost all quantum supremacy tasks (e.g.,~\cite{Boson, IQP, nature-google}) are sampling ones strengthens the importance of delegation for quantum sampling problems.
 %Even though the relation between $\BQP$ and $\SampBQP$ is relatively understood in the plain model,
 \Ethan{Maybe replace the following sentence with the actual challenges? Ie. unclear how to run many copies to reduce errors; classical approach with PRG seed doesn't work either}
However, it is far from clear whether the subtle difference between $\BQP$ and its sampling version could lead to
technical barrier in the context of CVQC, or
 %what are the potential technical challenges raised by their subtle differences in the context of CVQC and how to resolve them is however far from clear.
whether one can develop a CVQC protocol for $\SampBQP$ based on Mahadev's technique~\cite{FOCS:Mahadev18a}.

@@
